Catching runtime errors of Redis at compile time

### 2015-11-14 paper.tex
redis & hedis

\subsection{Hedis}
Redis can also be used in most programming languages, with 3rd party libraries
or packages that talk with Redis' TCP protocol. In Haskell, the most popular
package people are using is \emph{Hedis}.

The previous example in Redis's client would look something like this with Hedis
in Haskell.
\begin{minted}{haskell}
program :: Redis (Either Reply [ByteString])
program = do
    sadd "some-set" ["a", "b"]
    sadd "another-set" ["a", "b", "C"]
    sinter ["some-set", "another-set"]
\end{minted}

Function \mintinline{haskell}{sadd} takes a key and a list of values and returns an
\mintinline{haskell}{Integer},
wrapped in the context \mintinline{haskell}{Redis (Either Reply Integer)}
to which encapsulates possible failures.

 to indicate it's size. \mintinline{haskell}{sinter}
takes a list of keys and returns

 , both of type
  \mintinline{haskell}{ByteString}, and returns a \mintinline{haskell}{Integer}
  to indicate it's size.

  since keys and values are all just binary strings in Redis.

 and \mintinline{haskell}{sinter} now

\begin{minted}{haskell}
sadd :: ByteString      -- key
    -> [ByteString]     -- values
    -> Redis (Either Reply Integer)
sinter :: [ByteString]  -- keys
    -> Redis (Either Reply [ByteString])
\end{minted}

>>>>

\subsection{Hedis}
Redis can also be used in most programming languages, with 3rd party libraries
or packages that talk with Redis' TCP protocol. In Haskell, the most popular
package is \emph{Hedis}.

The previous example in Redis's client would look something like this with \emph{Hedis}
in Haskell.
\begin{minted}{haskell}
program :: Redis (Either Reply [ByteString])
program = do
    sadd "some-set" ["a", "b"]
    sadd "another-set" ["a", "b", "C"]
    sinter ["some-set", "another-set"]
\end{minted}

Function \mintinline{haskell}{sadd} takes a key and a list of values as arguments
, and returns an \mintinline{haskell}{Integer}, wrapped in
\mintinline{haskell}{Either} to indicate possible failures in
the context \mintinline{haskell}{Redis} of command execution.

\begin{minted}{haskell}
sadd :: ByteString      -- key
    -> [ByteString]     -- values
    -> Redis (Either Reply Integer)
\end{minted}

Keys and values are of type \mintinline{haskell}{ByteString}, since they are all
just binary strings in Redis. That means if a user wants to store values of
arbitrary types, he or she will have to encode and decode them as
 \mintinline{haskell}{ByteString}s.
